A Case Study in Preserving a High Energy Physics Application

### 2014-03-13 paper.tex
figure size modify

\begin{figure}
\centering
\epsfig{file=solution3.eps, height=2in, width=3in}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

@@

\subsection{Workflow of Packaging Utility}
\begin{figure*}
\centering
\epsfig{file=workflow-parrot.eps, height=4in, width=6.5in}
\caption{Workflow of Solution 4}
\label{fig:workflow-parrot}
\end{figure*}

@@

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package is as follows. 
{\tt package-utility.sh} is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
symbolic link files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

@@

\begin{figure}
\centering
\epsfig{file=preservation-integration.eps, height=2.2in, width=3.3in}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{solution3.eps}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

@@

\subsection{Workflow of Packaging Utility}
\begin{figure*}
\centering
\includegraphics[width=1.6\columnwidth]{workflow-parrot.eps}
\caption{Workflow of Solution 4}
\label{fig:workflow-parrot}
\end{figure*}

@@

The command used to generate the package is as follows. 
{\tt package-utility.sh} is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
symbolic link files) and the system call type.
The package description information is shown in Table~\ref{table:package-info}.

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
     the total size of package&21GB \\ \hline
    the total number of files&15905\\ \hline
    the total number of directory&1549\\ \hline
    the total number of symbolic link&4614 \\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{preservation-integration.eps}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure}
